---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", warning = FALSE, message = FALSE)
library(sagui)
```

Sagui separates four operations: prepare a common multiband cube, construct a
spatial support, assign categorical regions, and measure regional SEDs. Keeping
those operations explicit makes the result easier to reproduce.

## Install

```{r install, eval=FALSE}
install.packages("remotes")
remotes::install_github("RafaelSdeSouza/sagui", upgrade = "never")
library(sagui)
```

## Simulate a galaxy

This fixed-seed example mixes bulge, disc, and two knot profiles in nine bands.
It is an API demonstration, not an observation or a physical inference.

```{r simulate}
set.seed(42)
bands <- c(0.90, 1.15, 1.50, 1.82, 2.00, 2.77, 3.56, 4.10, 4.44)
nx <- ny <- 24L
xy <- expand.grid(x = seq_len(nx), y = seq_len(ny))
dx <- xy$x - 12.5
dy <- xy$y - 12.5
radius <- sqrt((dx / 1.10)^2 + (dy / 0.78)^2)
support <- matrix((dx / 11)^2 + (dy / 8.3)^2 <= 1, nx, ny)

profiles <- rbind(
  bulge = c(0.58, 0.78, 1.02, 1.16, 1.14, 0.98, 0.82, 0.72, 0.66),
  disc  = c(0.82, 0.94, 1.04, 1.08, 1.05, 0.92, 0.84, 0.78, 0.74),
  knot1 = c(1.18, 1.11, 1.02, 0.96, 0.93, 0.88, 0.98, 0.91, 0.86),
  knot2 = c(1.08, 1.04, 0.99, 0.95, 0.94, 0.91, 1.05, 0.99, 0.93)
)
weights <- cbind(
  exp(-(radius / 3.0)^2),
  exp(-radius / 8.5),
  exp(-((dx - 4.5)^2 + (dy + 1.8)^2) / 5),
  exp(-((dx + 4.0)^2 + (dy - 2.6)^2) / 6)
)
weights <- weights / rowSums(weights)
brightness <- 0.12 + 1.35 * exp(-radius / 8)
flux <- brightness * (weights %*% profiles)
flux <- flux + matrix(rnorm(length(flux), sd = 0.012), nrow(flux))
cube <- array(flux, c(nx, ny, length(bands)))
for (b in seq_along(bands)) cube[, , b][!support] <- NA_real_
```

## Segment

`use_starlet_mask = FALSE` is deliberate here because the simulated support is
already encoded by missing values outside the galaxy.

```{r segment}
seg <- segment_regions(
  cube,
  Ncomp = 6,
  use_starlet_mask = FALSE,
  cluster_pretransform = "none"
)
table(seg$cluster_map, useNA = "ifany")
```

Positive integers are categorical identifiers. Their ordering carries no
physical meaning; `NA` denotes unassigned background.

## Measure SEDs

```{r photometry}
regional <- extract_region_sed(
  cube,
  seg$cluster_map,
  band_values = bands,
  sigma_band = rep(0.012, length(bands))
)
knitr::kable(head(regional$flux_long), digits = 4)
```

```{r first-run-figure, echo=FALSE, out.width="100%", fig.cap="Six categorical regions and their fixed-seed nine-band regional SEDs. Curves are normalised at 2 µm only for shape comparison."}
figure_path <- file.path(dirname(knitr::current_input(dir = TRUE)), "..", "man", "figures", "sagui-first-run-synthetic-sed.png")
knitr::include_graphics(figure_path)
```

Continue with [Prepare Photometry](preparing-psf-matched-photometry.html) for
observations, or [Export Regional SEDs](exporting-regional-seds.html) for the
downstream data contract.
