---
title: "SED Segmentation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SED Segmentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Sagui clusters one photometric SED per supported pixel. Support construction,
clustering transforms, and flux measurement remain separate.

## Exact Ward

```{r exact, eval=FALSE}
seg <- segment_regions(
  input = cube,
  Ncomp = 20,
  use_starlet_mask = TRUE,
  cluster_pretransform = "none"
)
```

Exact Ward clustering stores all pairwise distances. Use it only when the
supported pixel count fits available memory.

## Sparse Ward

```{r sparse, eval=FALSE}
seg <- segment_regions_large(
  input = cube,
  Ncomp = 20,
  use_starlet_mask = TRUE,
  cluster_pretransform = "none",
  knn_k = 40,
  auto_k = FALSE
)
```

The sparse backend restricts candidate merges to a nearest-neighbour graph.
Record `knn_k`, `auto_k`, the support, and every transform alongside the result.

## Choose transforms

Use `cluster_pretransform`, not the deprecated `pretransform` alias. The
default `"none"` preserves the input representation. Alternatives such as
`"copula_gaussian"` change the clustering geometry and should be justified and
tested as analysis choices.

Region labels are categorical. Never map their integer values to an ordered
colour scale or interpret a larger label as a larger physical quantity.
