---
title: "Prepare Photometry"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Prepare Photometry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Sagui expects a numeric array with dimensions `[x, y, band]`, or a FITS-like
list with that array in `imDat`. Before segmentation, every band should refer to
the same sky footprint and effective angular resolution.

## Required checks

1. Register every image to one pixel grid and WCS.
2. Match all bands to a declared target PSF.
3. Convert fluxes and uncertainties to compatible units.
4. Keep the band order and effective wavelengths together.
5. Record missing-data and foreground-mask conventions.

Sagui does not perform image registration or PSF matching.

## Assemble the cube

```{r assemble, eval=FALSE}
band_files <- c("F090W.fits", "F150W.fits", "F200W.fits", "F356W.fits")
bands <- c(0.90, 1.50, 2.00, 3.56)

planes <- lapply(band_files, function(path) FITSio::readFITS(path)$imDat)
stopifnot(length(unique(lapply(planes, dim))) == 1L)
cube <- simplify2array(planes)
```

Apply the same geometric operations to the variance planes. Measure fluxes
from the calibrated images, not display stretches.

## Validate

```{r validate, eval=FALSE}
stopifnot(length(dim(cube)) == 3L)
stopifnot(dim(cube)[3] == length(bands))
stopifnot(all(dim(var_cube) == dim(cube)))
```

Next, define the pixels to segment with a [support mask](support-mask-construction.html).
