---
title: "Support Masks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Support Masks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A support mask decides which pixels are eligible for segmentation. It is not a
segmentation map.

## Starlet support

The default path collapses the cube, reconstructs selected starlet scales, and
thresholds the result.

```{r starlet, eval=FALSE}
support <- build_starlet_mask(
  input = cube,
  starlet_J = 5,
  starlet_scales = 2:5,
  denoise_k = 2.5,
  positive_only = TRUE
)
image(support$mask)
```

The support depends on the collapse function, scale range, threshold, and
cleanup settings.

## Adaptive support

`build_adaptive_support()` combines evidence across bands. It is useful when no
single collapse represents the source adequately.

```{r adaptive, eval=FALSE}
support <- build_adaptive_support(cube, pretransform = "none")
```

For directional structures, `build_contourlet_mask()` provides an alternative
to starlets. Compare both masks before segmentation.

## Background values

Use `FALSE` in a logical support. The segmentation functions return unassigned
background as `NA` in `cluster_map`.
